Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-09-27 ejap.manuscript.RMD
small updates

@@

### Perspectives and Significance

@@

# DATA AVAILABILITY

@@

# SUPPLEMENTAL MATERIAL

@@

# AUTHOR CONTRIBUTIONS
Conceived and designed research: SE, HH, DH.
Performed experiments: KL, DH, HH, HN, SCM.
Interpreted results of experiments: KL, DH.
Prepared Figures: KL, DH.
Drafted manuscripts: KL, DH.
Edited and revised manuscript: SE, HH, DH.
Approved final version of the manuscript: .

# References

>>>>

## Acknowledgements
Great thanks are in order to Henriette Spilhaug Bollandsås, Nora Lerdalen Bonsak and Thea Bøhn Nyløkken for their impressive commitment and dedication in the training intervention
the Inland Norway University of Applied Sciences, for funding this research. Gratitude is also due to Daniel Hammarström, Håvard Hamarsland and Prof. Stian Ellefsen for the guidance and <!-- needs more work -->

@@

### Conclusion

@@

## DATA AVAILABILITY

@@

## SUPPLEMENTAL MATERIAL

@@

## AUTHOR CONTRIBUTIONS
Conceived and designed research: SE, HH, DH.
Performed experiments: KL, DH, HH, HN, SCM.
Interpreted results of experiments: KL, DH.
Prepared Figures: KL, DH.
Drafted manuscripts: KL, DH.
Edited and revised manuscript: SE, HH, DH.
Approved final version of the manuscript: .

## References
